SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-05 related.tex
missing prefetchers

Two widely used prefetchers are ?Next-n Lines? \cite{nextnlines} and Stride [4], both of which capture regular memory access patterns with very low hardware overhead. The ?Next-n Lines? prefetcher simply queues prefetches for the next n lines after any given miss, under the expectation that the principle of spatial locality will hold and those cache lines after a missed line are likely to be used in the future. The stride prefetcher is slightly more sophisticated; it attempts to identify simple stride reference patterns in programs based upon the past behavior of missing loads. Similar to the ?Next-n Lines? technique, when a given load misses, cache lines ahead of that miss are fetched in the pattern following the previous be- havior in the hope of avoiding future misses. Both prefetch- ers have been widely used due to the simple design and low hardware overhead. However, without further knowledge about temporal locality and application characteristics, these prefetchers cannot do more than detecting and prefetching regular memory access patterns with limited spatial locality.

Somogyi et al. proposed one of the current top- performing, practical, low-overhead prefetchers, the Spatial Memory Streaming (SMS) prefetcher [23]. SMS leverages code-based correlation to take advantage of spatial locality in the applications over larger regions of memory (called spatial regions). It predicts the future access pattern within a spatial region around a miss, based on a history of access patterns initiated by that missing instruction in the past. While the SMS prefetcher is effective, it is indirectly inferring future program control-flow when it speculates on the misses in a spatial region. As a result, the state overheads of this predictor can be higher than the others in this class.

@@

%ANMP

@@

>>>>

Two widely used prefetchers are Next-n Lines \cite{nextnlines} and Stride \cite{stride}, both of which capture regular memory access patterns with very low hardware overhead. The Next-n Lines prefetcher simply queues prefetches for the next n lines after any given miss, under the expectation that the principle of spatial locality will hold and those cache lines after a missed line are likely to be used in the future. The stride prefetcher is slightly more sophisticated; it attempts to identify simple stride reference patterns in programs based upon the past behavior of missing loads. Similar to the Next-n Lines technique, when a given load misses, cache lines ahead of that miss are fetched in the pattern following the previous behavior in the hope of avoiding future misses. Both prefetchers have been widely used due to the simple design and low hardware overhead. However, without further knowledge about temporal locality and application characteristics, these prefetchers cannot do more than detecting and prefetching regular memory access patterns with limited spatial locality.

Somogyi et al. proposed one of the top practical, low-overhead prefetchers, the Spatial Memory Streaming (SMS) prefetcher \cite{sms}. SMS leverages code-based correlation to take advantage of spatial locality in the applications over larger regions of memory (called spatial regions). It predicts the future access pattern within a spatial region around a miss, based on a history of access patterns initiated by that missing instruction in the past. While the SMS prefetcher is effective, it is indirectly inferring future program control-flow when it speculates on the misses in a spatial region. As a result, the state overheads of this predictor can be higher than the others in this class.

@@

To address both prefetching coverage and accuracy, prior work has adopted lookahead 
mechanisms. Lookahead prefetchers efficiently encode the relationship between accesses to yield future predictions, enabling further speculative lookahead accesses.
VLDP \cite {vldp} prefetches a static depth ahead of the demand fetch, without considering the prefetching confidence,

DA-AMPM

@@

%not sure this is where this section was going, I just kidna went with it.
